Constructing Sailing Match Race Schedules: Round-Robin Pairing Lists

### 2015-06-22 paper.tex
Mark special edge with a star

\paragraph{State transitions:} The $\state$ variables are then used to impose match race criterion~4
(if last in flight $i$ then not first in flight $i+1$), criterion~11 (if last in flight $i$ then not
in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i+1$ is not first).
These criteria are imposed by \eqref{C3}, which is a deterministic finite automaton (DFA) constraint, i.e. Pesant's \emph{regular} constraint 
\cite{Pesant04}. The transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
represent a possible transition from one state to another. The DFA is encoded as a set of transition objects
$\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to state $q_{j}$
when encountering input~$\iota$. In addition we specify the accepting states, which are all states
except the start state (white) and the bye state (pink).  This constraint also ensures that if a
skipper has finished all matches in flight $i$ (i.e.\ is in state $\END$) then that skipper will also have
finished all matches in flight $i+1$ (and so on). Note that when we have as many boats as skippers directed edge $(\BYE,\LAST)$ becomes bidirectional.

@@

        \draw [<-, >=latex, thick] (DFAL) to (DFAB);

@@

    \end{tikzpicture}
    \caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey
        timeslots. The schedule for skipper 5 is in bold and the DFA for
        criteria~4, 11 and~12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in
        yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}\label{skipper5}
\end{figure}

>>>>

\paragraph{State transitions:} The $\state$ variables are then used to impose match race criterion~4
(if last in flight $i$ then not first in flight $i+1$), criterion~11 (if last in flight $i$ then not
in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i+1$ is not first).
These criteria are imposed by \eqref{C3}, which is a deterministic finite automaton (DFA) constraint, i.e. Pesant's \emph{regular} constraint 
\cite{Pesant04}. The transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
represent a possible transition from one state to another. The DFA is encoded as a set of transition objects
$\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to state $q_{j}$
when encountering input~$\iota$. In addition we specify the accepting states, which are all states
except the start state (white) and the bye state (pink).  This constraint also ensures that if a
skipper has finished all matches in flight $i$ (i.e.\ is in state $\END$) then that skipper will also have
finished all matches in flight $i+1$ (and so on). Note that when we have as many
boats as skippers, the directed edge $(\BYE,\LAST)$ (marked $\star$) becomes bidirectional.

@@

        \draw [<-, >=latex, thick] (DFAL) to node [xshift=0.6em] { $\star$ } (DFAB);

@@

    \end{tikzpicture}
    \caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey
        timeslots. The schedule for skipper 5 is in bold and the DFA for
        criteria~4, 11 and~12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in
        yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red. The edge
        marked $\star$ is explained in the text.}\label{skipper5}
\end{figure}
